%============================================================
% MTH 111Z Project - Template File
% Section 5.6 from OpenStax OER
%	Updated 202302
%============================================================

\section{Graphs of Rational Functions} \label{functions-rational-graphs}

In this section, we'll continue working with rational functions.  We'll examine the long-term or end behavior and see what happens when there is a common root of the numerator and denominator.  We'll then use everything we've learned about rational functions to graph them, as well as construct rational functions based on a given graph.
      \\[0.5em]
\textbook{5.6}



\subsection*{Preparation Exercises} \label{prep-functions-rational-graphs}


\begin{myPrep}
Suppose a bakery has daily fixed costs of \$150.  To produce a single loaf of bread costs an additional \$2.75  for labor and materials.
\begin{enumerate}
\item Find a function that calculates the daily cost per loaf, $C$ in dollars, to produce $x$ loaves of bread.  \\
Hint: To find the cost per loaf, you need to divide the total costs by the number of loaves of bread.
\vfill
\item If the bakery produce 5 loaves of bread, what is the cost per loaf?  
\vfill
\item If the bakery produce 50 loaves of bread, what is the cost per loaf?
\vfill
\item If the bakery produce 500 loaves of bread, what is the cost per loaf?
\vfill
\item What is happening to the per loaf cost as the number of loaves made increases?
\vfill
\item Is there a limit to the how low the cost per loaf can go?
\vfill
\end{enumerate}
\end{myPrep}
